A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-07-24 vignette/Manuscript2Word.Rmd
Create vignette copy of manuscript from bookdown file, specifically for rendering into word. And the rendered word document plus styles template file

# Manuscript
<!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
<!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->

@@

There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Australian mungbean. 
Much of the experimental work has been published by funding agencies and state government extension departments as extension bulletins or other related type materials.
Past field trials in eastern Australia have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016]. 
Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017]. 
However due to the variability in the results between seasons and experiments few of these studies produced a clear result based on a statistical analysis. 
This variability presents uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.

<!--Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a;  insert all published trials here -->.

@@

```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref) %>%
   summarise(
      year = unique(year),
      location = unique(location),
      planting_date = unique(planting_date),
      first_sign_disease = unique(first_sign_disease)
   ) %>%
   arrange(year) %>%
   mutate(Research_org = c(
      rep("Queensland DAF", times = 4),
      rep("Northern Growers Alliance", times = 4),
      rep("Queensland DAF", times = 4),
      rep("USQ", times = 5)
   )) %>%
   kable(caption = "Table 1: Description of Experiments")
```
<br>
<br>
```{r Table2_1to9Scale, echo=FALSE}
data.frame(
   Scale = 1:9,
   `Scale Description` = c(
      "No sign of powdery mildew",
      "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
      "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
      "Colonies to top of the plant with > 75 % of plants affected",
      "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
   )
) %>%
   kable(caption = "Table 2: Powdery Mildew severity scoring scale") 
```
<br>

>>>>

***

<!-- need to ensure the format of this manuscript adheres to the MDPI Agronomy style guide -->
<!-- To ensure formatting matches, I suggest that you create a Word template and knit this document using that -->

@@

There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Australian mungbean. 
Much of the experimental work has been published by funding agencies and state government extension departments as extension bulletins or other related type materials.
Past field trials in eastern Australia have tested a range of fungicide active ingredients while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016]. 
Early trials showed that for fungicide applications to protect yield, a single fungicide application at first sign of the disease with another follow-up application two weeks later, if necessary, was the most effective [@SueThompson2016; @Sparks2017]. 
However, due to the variability in the results between seasons and experiments, few of these studies produced a clear result based on a statistical analysis. 
This variability presents uncertainty for the best practice of fungicide spray schedules to mitigate yield losses from powdery mildew.

<!--Some of the fungicides tested for controlling powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a;  insert all published trials here -->

@@

```{r Table1_ExperimentalDetail, echo=FALSE, message=FALSE, warning=FALSE}
PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole") %>%
   group_by(trial_ref) %>%
   summarise(
      year = unique(year),
      location = unique(location),
      planting_date = unique(planting_date),
      first_sign_disease = unique(first_sign_disease)
   ) %>%
   arrange(year) %>%
   mutate(Research_org = c(
      rep("Queensland DAF", times = 4),
      rep("Northern Growers Alliance", times = 4),
      rep("Queensland DAF", times = 4),
      rep("USQ", times = 5)
   )) %>%
   kable(caption = "Table 1: Description of Experiments", booktabs = T, align = "c")
```

<br>
<br>

```{r Table2_1to9Scale, echo=FALSE}
data.frame(
   Scale = 1:9,
   `Scale Description` = c(
      "No sign of powdery mildew",
      "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
      "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants affected",
      "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
      "Colonies to top of the plant with > 75 % of plants affected",
      "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
   )
) %>%
   kable(caption = "Table 2: Powdery Mildew severity scoring scale",  align = "cl") 
```
<br>
